\documentclass[11pt,a4paper]{article}
\usepackage{amsmath, amsthm, amsfonts, amssymb}
\usepackage{color}
\usepackage{bm}	
\usepackage{float}
\usepackage{caption, subcaption}
\usepackage{times}
\usepackage{fancyhdr}           % Allows better control over headers and footers
%\usepackage{layout}            % use with \layout to see the page layout for
%debugging purposes.
\usepackage[margin=2.5cm]{geometry}  %   set the margins using the
                                %   geometry package (which is much
                                %   the easiest way of doing this).
\usepackage[pdftex]{graphicx}   %   Pictures (means you have to
                                %   produce pdf output via pdflatex)
\usepackage[small,compact]{titlesec}   % Try to reduce the white space
                                % latex loves so much
\titlelabel{\thetitle. \quad}   % Reduce space around section heads
                                % and add a full stop after the number
\pagestyle{fancy}               % Invoke fancy headers

\renewcommand{\abstractname}{\vskip -5mm}  %  Change name of Abstract
                                %  to nothing and loose some of the
                                %  excessive white space
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\newcommand{\tab}[1]{\hspace{.2\textwidth}\rlap{#1}}

\begin{document}
    \begin{titlepage} \begin{center}
            \textsc{\LARGE University of Cape Town}
            \\[1.5cm] \textsc{\Large Software Engineering Stage Four} \\\smallskip
            \textsc{\Large Work Allocation} \\\smallskip
            \textsc{\Large CSC3003S} \\\smallskip
            \textsc{\Large \today} \\\smallskip
            \noindent\rule[0.4mm]{\textwidth}{0.1mm}
            \\[0.4cm] { \huge \bfseries Tempest Trace \\[0.4cm] }
            \noindent\rule[0.4mm]{\textwidth}{0.1mm}
            \\[1cm]
            \begin{minipage}[t]{0.4\textwidth}
                \begin{flushleft}\large \emph{Authors:}\\ Brian Mc George - MCGBRI004 \\ Jacques Heunis - HNSJAC003 \\ Timothy Gwynn - GWYTIM001
                    \\[2cm]
                \end{flushleft}
            \end{minipage} \begin{minipage}[t]{0.4\textwidth}
            \begin{flushright} \large \emph{Supervisor:} \\ Assoc. Prof.~Patrick Marais\\patrick@cs.uct.ac.za\end{flushright}
            \begin{flushright} \large \emph{Tutor:} \\ Codie Roelf\\Codie.Roelf@alumni.uct.ac.za\end{flushright}
        \end{minipage}
    \end{center}
\end{titlepage}

%%%  Set the headers via fancyhdr package
\lhead{Capstone Project 2015}  % Short title for running head
\chead{}
\rhead{\today}   %  Fixed running head of the date
\lfoot{}
\cfoot{\thepage}    %  add page number as centre footer.
\rfoot{}
\renewcommand{\headrulewidth}{0.0pt}   % Don't want horizontal line
                                % under header.
\section{Brian Mc George - MCGBRI004}
\subsection{Project}
\begin{enumerate}
    \item All work relating to drone (except drone model) and sniper
    \item Scripted all intractables in the game:\\
    Created all of the smoke bomb related scripts and its particle effects.\\
    Made doors open-able.\\
    Created all of air conditioning: player slow script that can slow the player and particle effects\\
    Added all scripting work for elevator: elevator slow interactions, added the particle effect, closed door etc.
    \item Added all heads-up display elements: HUD sway, game clock and position calculations.
    \item Added all camera effects: Headbob and the hit effect that plays when hit by a bullet.
    \item Added all current sounds
    \item Added checkpoints
    \item Added player life handler (controlling player death - screen fades out when player dies, re-spawns player at last checkpoint passed and then clears screen)
    \item Added player health script (allow player to take damage and regenerate health)
    \item Added an intro fly-over script (currently not implemented - awaiting intro dialog)  
\end{enumerate}
\subsection{Report}
\begin{enumerate}
    \item Design Analysis section (section 3) - including the design class diagram and architecture diagram.
    \item All of the implementation section (section 4.2+) excluding the sections relating to the player controller (section 4.1).\\
          Created the decision tree diagrams for drone and sniper and graph of the offset functions.
    \item Provided a number of the validation tests which were created for Stage 3.
    \item Improve the format of the user manual and add the back-story and getting started section.
    \item Added Analysis artefacts produced (section 2.4).
    \item Updated some of the use case narratives to be up-to-date.
    \item Joint edited the document with Jacques.
\end{enumerate}
\section{Jacques Heunis - HNSJAC003}
\textbf{Game:} All scripts relating to control of the player avatar. More specifically the two mouselook scripts, the movement script, and the InputSplitter class. \\
\textbf{Report:} Introduction and Conclusion sections as well as the subsections of Implementation section that pertain to the character controller.
\section{Timothy Gwynn - GWYTIM001}
\subsection{Game}
\subsubsection{Level Design}
Each gameplay section designed independantly, co-designed with Brian Mc George.
\subsubsection{Level Creation}
Actualised Level design components in Unity, added detail as neccassary, created all scenery related buildings.
\subsubsection{Mechanic Design}
Gave input on mechanics needed to take advantage of the obstacles in the level, provided feedback on changes needed after testing.
\subsubsection{Testing}
Tested each new section of the world as it was created, tested new mechanics on level created at the time as they were introuced
\subsection{Report}
Abstract, Requirements captured, Program Validation and Verification, User Manual - co done with Brian Mc George
\end{document}



